Pillar 1 - Sequential Pattern Mining

### 2019-02-13 Pillar 1 - Sequential Pattern Mining.Rmd
debug
adds comments

### take -> take
```{r AR take}
AR <- list()

@@

### fail -> fail
```{r AR fail}
AR$PF <- transactions$PF %>%

@@

### low grade -> low grade
```{r AR low}
AR$HL <- transactions$HL %>%

@@

### not take -> fail
```{r AR TPF}
AR$TPF <- transactions$TPF %>%

@@

### grade less than or equal to x -> grade less than or equal to 6
```{r AR grade, cache = TRUE}
AR$G <- transactions$G %>%

@@

### Editing AR
```{r edit_AR}
edit_rules <- function(AR){

@@

# Remove objects
rm(
  my_apriori, make_AR,
  AR, transaction
  )
```

>>>>

}
```
###Apply Functions
We apply make_AR to get different sets of rules:

#### take -> take
```{r AR take}
AR <- list()

@@

#### fail -> fail
```{r AR fail}
AR$PF <- transactions$PF %>%

@@

#### low grade -> low grade
```{r AR low}
AR$HL <- transactions$HL %>%

@@

#### not take -> fail
```{r AR TPF}
AR$TPF <- transactions$TPF %>%

@@

#### grade less than or equal to x -> grade less than or equal to 6
```{r AR grade, cache = TRUE}
AR$G <- transactions$G %>%

@@

### Editing AR
The function edit_rules makes AR easier to read. It keeps only rules that appear more than 5 times, rounds numerical variables to 5 significant digits, and drops aiding columns which were only used for computation in previous stages but add no additional information.
```{r edit_AR}
edit_rules <- function(AR){

@@

# Remove objects
rm(
  my_apriori, make_AR,
  AR, transaction
  )
